---
title: "pm3148 - Homework 1"
output: html_notebook
---
Import Libraries
```{r}
library(tidyverse)
library(palmerpenguins)
```


Problem 1: 
#This problem is intended to emphasize variable types and introduce coercion; some awareness of how R treats numeric, character, and factor variables is necessary for working with these data types in practice.

#Create a data frame comprised of:

#a random sample of size 10 from a standard Normal distribution
#a logical vector indicating whether elements of the sample are greater than 0
#a character vector of length 10
#a factor vector of length 10, with 3 different factor “levels”
```{r}

set_seed(123)
example_df = 
  tibble(
    x = rnorm(10, mean =1),
    log_vec = if(x>0) {TRUE} else {FALSE},
    vec_char = c("char1", "char2", "char3", "char4", "char5", "char6","char7","char8","char9","char10"), 
    vec_factor = factor(c("level1", "level2", "level3","level1", "level2", "level3","level1", "level2", "level3","level1"))
  )

view(example_df)

#Take mean of each variable
mean(example_df$x)
mean(example_df$log_vec)
mean(example_df$vec_char)
mean(example_df$vec_factor)


example_df%>%
  pull(x)%>%
  mean()

example_df%>%
  pull(log_vec)%>%
  mean()

example_df%>%
  pull(vec_char)%>%
  mean()

example_df%>%
  pull(vec_factor)%>%
  mean()
```


Problem 2
```{r}
data(package = 'palmerpenguins')

head(penguins)
str(penguins)
```
#There are 8 variables in this dataset. The variables are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. 

```{r}
paste("There are", (nrow(penguins)), "rows in the penguins dataset")
paste("There are", (ncol(penguins)), "columns in the penguins dataset")

penguins%>%
  pull(flipper_length_mm)%>%
  mean(na.rm=TRUE)
```

```{r}
penguins%>%
  ggplot(aes(x = bill_length_mm, y =flipper_length_mm, color = species)) + geom_point()
ggsave(filename = "bill_lengthvflipper_length.png")
```

