---
title: "pm3148 - Homework 1"
output:
  html_document:
    df_print: paged
---


Import Libraries
```{r}
library(tidyverse)
library(palmerpenguins)
```


# Problem 1: 

Create a data frame comprised of:
a random sample of size 10 from a standard Normal distribution
a logical vector indicating whether elements of the sample are greater than 0
a character vector of length 10
a factor vector of length 10, with 3 different factor “levels”
```{r}
#Set seed to replicate results from rnorm 
set.seed(123)

#Create dataframe based on previous requirements 
example_df = 
  tibble(
    x = rnorm(10, mean =1),
    log_vec = if(x>0) {TRUE} else {FALSE},
    vec_char = c("char1", "char2", "char3", "char4", "char5", "char6","char7","char8","char9","char10"), 
    vec_factor = factor(c("level1", "level2", "level3","level1", "level2", "level3","level1", "level2", "level3","level1"))
  )

view(example_df)

##Mean of X
example_df%>%
  pull(x)%>%
  mean()

##Mean of logical vector
example_df%>%
  pull(log_vec)%>%
  mean()

##Mean of character vector
example_df%>%
  pull(vec_char)%>%
  mean()

##Mean of factor vector
example_df%>%
  pull(vec_factor)%>%
  mean()
```

```{r eval=FALSE}
#Convert all variables to numeric 
example_df$x_num<- as.numeric(example_df$x)
example_df$log_vec_num<- as.numeric(example_df$log_vec)
example_df$vec_char_num<-as.numeric(example_df$vec_char)
example_df$vec_factor_num<-as.numeric(example_df$vec_factor)

##Mean of X
example_df%>%
  pull(x_num)%>%
  mean()

##Mean of logical vector
example_df%>%
  pull(log_vec_num)%>%
  mean()

##Mean of character vector
example_df%>%
  pull(vec_char_num)%>%
  mean()

##Mean of factor vector
example_df%>%
  pull(vec_factor_num)%>%
  mean()

```
The mean function can only take in numeric data. In order for the factor variable mean to be calcualted, the factors had to be converted to numbers/levels. The character variable could not be converted to a number so all the values got converted to NA values. Then the mean function could not calculate a mean to do the missing values. 


# Problem 2
```{r}
#Load data and view
data(package = 'palmerpenguins')

head(penguins)
str(penguins)
```
There are 8 variables in this dataset. The variables are species, island, bill_length_mm, bill_depth_mm, flipper_length_mm, body_mass_g, sex, and year. 

There are `r nrow(penguins)` rows in the penguins dataset. 
There are `r ncol(penguins)`columns in the penguins dataset. 
The mean flipper length is `r penguins%>%pull(flipper_length_mm)%>% mean(na.rm=TRUE)` mm. 
```{r eval=FALSE}
nrow(penguins)
ncol(penguins)

#Mean of flipper_length
penguins%>%
  pull(flipper_length_mm)%>%
  mean(na.rm=TRUE)
```
The mean flipper length in mm is 200.9152 mm. 
```{r}
#Scatter plot 
penguins%>%
  ggplot(aes(x = bill_length_mm, y =flipper_length_mm, color = species)) + geom_point()
ggsave(filename = "bill_lengthvflipper_length.png")
```

